### 2015-05-24 docs/report/array_partitioning.tex
Benchmark link fixes

\subsubsection{\ttarray{} copy benchmark}
A benchmark was created based on the aforementioned alternatives:
\bmcode{http://jsperf.com/arraybuffer-copy}{../../spikes/2.3.1/copyComparison.js}

@@

\subsubsection{\ttarray{} split benchmark}
Based on the result from the previous benchmark we created a new benchmark to understand which alternative is better to partition an array into parts:
\bmcode{http://jsperf.com/arraybuffer-copy}{../../spikes/2.3.1/splitComparison.js}

>>>>

\subsubsection{\ttarray{} copy benchmark}
A benchmark was created based on the aforementioned alternatives:
\bmcode{http://jsperf.com/arraybuffer-copy/4}{../../spikes/2.3.1/copyComparison.js}

@@

\subsubsection{\ttarray{} split benchmark}
Based on the result from the previous benchmark we created a new benchmark to understand which alternative is better to partition an array into parts:
\bmcode{http://jsperf.com/arraybuffer-split/3}{../../spikes/2.3.1/splitComparison.js}

### 2015-05-24 docs/report/function_caching.tex
Benchmark link fixes

\section{Function caching}

@@

To verify its performance we created a benchmark that runs with and without the function cache:
\bmcode{http://jsperf.com/p-j-s-with-vs-without-function-cache}{../../spikes/3.1.3/functionCache/functionCache.js}

@@

\subsection{Conclusion}
As the benchmark shows versions 40 and 41 of chrome have almost no difference between the implementations with and without the cache. To determine whether introducing the cache was worth it or not we also used Chrome Canary version 42. The latter shows a big increase in performance (near 20\%), which is why we decided to leave the \tfunction{} cache as part of our implementation.

>>>>

\section{Function caching}\label{sec:func-caching}

@@

To verify its performance we created a benchmark that runs both with and without the function cache:
\bmcode{http://jsperf.com/p-j-s-with-vs-without-function-cache/3}{../../spikes/3.1.3/functionCache/functionCache.js}

@@

\subsection{Conclusion}
As the benchmark shows versions 40 and 41 of Google Chrome have almost no difference between the implementations with and without the cache. To determine whether introducing the cache was worth it or not we considered the result from Firefox Nightly, which shows a big increase in performance (near 25\%), which is why we decided to make the \tfunction{} cache a part of our implementation.
